%% sections/a-one-page-summary.tex - H. R. 9510 Bill v4.0 (full bill) - Appendix A
%% Genre: executive one-pager (labeled blocks). Source deliverable 01. Table 5.
\billsec{APPENDIX A.}{ONE-PAGE SUMMARY (NON-OPERATIVE).}\phantomsection\label{toc:aA}

\uscprov{1}{\textit{Independent research draft. Bill: H. R. 9510 (illustrative
number; the Clerk assigns the real number at introduction), 119th Congress, 2d
Session. Refer to: House Committee on Energy and Commerce (Subcommittee on
Health).}}

\uscprov{1}{\textbf{The problem: a sequencing gap that embodiment makes dangerous.}
Physical AI oncology trials place autonomous and semi-autonomous robots in direct
physical contact with patients, and the robot's behavior at the moment of contact
is set by software that is increasingly machine-generated. No Federal law governs
the order of operations, so a sponsor may generate robot-patient interaction code,
run it, and document the checks afterward. In a disembodied data pipeline an error
yields a wrong number a human can catch downstream; in an embodied surgical system
the same error class yields a wrong motion no human can catch in time.}

\uscprov{1}{\textbf{The solution: verify before generate, in a new section 515D.}
The bill adds a new section 515D to the Federal Food, Drug, and Cosmetic Act (21
U.S.C. 360e-5), inserted right after the predetermined change control plan
authority (section 515C, 21 U.S.C. 360e-4). No robot-patient interaction code may
be generated or executed unless an automated verification, validation, and
uncertainty quantification process, bound to named external standards, has first
cleared, with the record documented and attested. Each gate emits ACCEPT, BLOCK, or
ESCALATE; the verification fraction must equal 1.0; and three gates carry a hard
catastrophe predicate at agreement 1.00.}

\uscprov{1}{\textbf{What it changes: ten conforming amendments.} Ten targeted edits
thread the rule through Title 21: sections 201(h), 301, 501, 505F, 510(k), 513, 515,
515C, 520(o), and 521, so the new rule is enforceable and consistent with existing
device law \cite{usc-321h, usc-331, usc-351, usc-360c, usc-360e}.}

\uscprov{1}{\textbf{The assurance evidence.} VVUQ-01 held the verification fraction
at 1.0 across 51 of 51 tests, accepting 1 candidate and blocking 5, with 1
escalation. VVUQ-02 cleared all 10 gates over a surgical-humanoid control codebase:
172 of 172 tests, 32 of 32 sweep iterations, composite mean 93.56, reproducible
from deterministic seed 20260525 \cite{kawchak2026vvuq01, kawchak2026vvuq02}.}

\uscprov{1}{\textbf{In-force analogues and cost.} The approach builds on the section
515C change control plan authority and the FDA final PCCP guidance, the Quality
Management System Regulation (21 CFR part 820, effective February 2, 2026), 21 CFR
part 11, and the Medicare Advantage human-over-AI guardrail (42 CFR 422.101(c)). It
directs final regulations within 365 days and creates no new spending program, so
it is expected to be PAYGO neutral \cite{fda-pccp-2024, fr-qmsr-2024, cms-4201-ma}.}

\uscprov{1}{Table 5 condenses the one-page summary into a block table.}

{\footnotesize
\begin{xltabular}{\textwidth}{@{}L{3.0cm} Y@{}}
\hline\noalign{\vskip 0.04cm}
\textbf{Block} & \textbf{In one line}\\
\hline\noalign{\vskip 0.04cm}
\endfirsthead
\hline\noalign{\vskip 0.04cm}
\textbf{Block} & \textbf{In one line}\\
\hline\noalign{\vskip 0.04cm}
\endhead
\hline\noalign{\vskip 0.04cm}
\endlastfoot
Problem & No Federal rule makes verification precede generation of robot-patient
code; embodiment turns a wrong number into a wrong motion\\
\hline\noalign{\vskip 0.04cm}
Rule & New section 515D: clear an automated, standards-bound VVUQ gate before
generating or executing the code\\
\hline\noalign{\vskip 0.04cm}
Reach & Ten conforming amendments thread the rule through Title 21\\
\hline\noalign{\vskip 0.04cm}
Evidence & 51 of 51 and 172 of 172 tests; ten gates; composite 93.56; seed
20260525\\
\hline\noalign{\vskip 0.04cm}
Cost & Rulemaking only; expected PAYGO neutral\\
\hline\noalign{\vskip 0.04cm}
The ask & A House sponsor to introduce and refer to Energy and Commerce\\
\hline
\end{xltabular}}
\vspace{-0.8cm}
\figcaption{Table 5. The one-page summary as a block table: the problem, the rule,
its reach, the evidence, the cost, and the ask.}
