%% sections/s4-comparative.tex - H. R. 9510 Bill v4.0 (full bill)
%% SEC. 4. COMPARATIVE PRINT; CHANGES IN EXISTING LAW.
%% Gray-scale Mermaid figure (TikZ): Figure 5 (affected sections in order).
%% Table 4 (per-section change map) and the reproduced provisions with markers.
\billsec{SEC. 4.}{COMPARATIVE PRINT; CHANGES IN EXISTING LAW.}\phantomsection\label{toc:s4}

\uscprov{1}{\textbf{(a) Reader's Note on Conventions.} This section shows, in
comparative print, the changes the amendment makes to existing law. Existing text
is plain; matter proposed to be struck is shown \cprstrike{a strike marker}; matter
proposed to be inserted is shown \cprinsert{an insert marker}. No strikethrough or
underline is used. Table 4 is the per-section change map, and Figure 5 shows the
eleven affected sections in comparative-print order.}

{\footnotesize
\begin{xltabular}{\textwidth}{@{}L{1.8cm} L{2.0cm} Y@{}}
\hline\noalign{\vskip 0.04cm}
\textbf{FD\&C \S} & \textbf{21 U.S.C.} & \textbf{Nature of the marked change}\\
\hline\noalign{\vskip 0.04cm}
\endfirsthead
\hline\noalign{\vskip 0.04cm}
\textbf{FD\&C \S} & \textbf{21 U.S.C.} & \textbf{Nature of the marked change}\\
\hline\noalign{\vskip 0.04cm}
\endhead
\hline\noalign{\vskip 0.04cm}
\endlastfoot
new \S~515D & \S~360e-5 & Insert the entire new section (verify before generation)\\
\hline\noalign{\vskip 0.04cm}
\S~201(h) & \S~321(h) & Insert reach to robot-patient interaction code\\
\hline\noalign{\vskip 0.04cm}
\S~301 & \S~331 & Insert a new prohibited act paragraph\\
\hline\noalign{\vskip 0.04cm}
\S~501 & \S~351 & Insert an adulteration trigger for a missing 515D record\\
\hline\noalign{\vskip 0.04cm}
\S~505F & \S~355g & Insert recognition of 515D records in the RWE program\\
\hline\noalign{\vskip 0.04cm}
\S~510(k) & \S~360(k) & Insert a verification-governed-change exception\\
\hline\noalign{\vskip 0.04cm}
\S~513 & \S~360c & Insert graduated special controls by degree of autonomy\\
\hline\noalign{\vskip 0.04cm}
\S~515 & \S~360e & Insert the cleared record into the PMA contents\\
\hline\noalign{\vskip 0.04cm}
\S~515C & \S~360e-4 & Insert an automated verification-before-change protocol\\
\hline\noalign{\vskip 0.04cm}
\S~520(o) & \S~360j(o) & Insert a carve-back excluding robot-control software\\
\hline\noalign{\vskip 0.04cm}
\S~521 & \S~360k & Insert a State human-in-the-loop savings clause\\
\hline
\end{xltabular}}
\vspace{-0.8cm}
\figcaption{Table 4. Per-section comparative-print change map: the new section and
the ten conforming amendments, each by Federal Food, Drug, and Cosmetic Act
section, 21 U.S.C. citation, and the nature of the marked change.}

\begin{mermaidfig}
\node[mmin,text width=22mm]  (a) at (0,0)    {\S 321 definitions};
\node[mmin,text width=22mm]  (b) at (2.7,0)  {\S 360c classification};
\node[mmstep,text width=22mm](c) at (5.4,0)  {\S 360e PMA};
\node[mmlaw,text width=22mm] (d) at (8.1,0)  {\S 360e-4 PCCP};
\node[mmgoal,text width=22mm](e) at (10.8,0) {\S 360e-5 NEW};
\node[mmin,text width=40mm]  (f) at (5.4,-1.9) {\S 331, 351, 355g, 360(k), 360j(o), 360k conforming};
\draw[mmedge] (a)--(b); \draw[mmedge] (b)--(c); \draw[mmedge] (c)--(d);
\draw[mmedge] (d)--(e); \draw[mmedge] (e) |- (f);
\end{mermaidfig}
\vspace{-0.3cm}
\figcaption{Figure 5. The eleven affected sections in comparative-print order: the
classification-to-approval spine, the new section 360e-5, and the conforming
amendments threaded through the rest of Title 21.}

\uscprov{1}{\textbf{(b) New Section 515D (21 U.S.C. 360e-5).} The following new
section is inserted after section 515C:}
\uscquote{0}{\cprinsert{Sec. 515D. Verification before generation of robot-patient
interaction code in Physical AI oncology investigations. (a) No robot-patient
interaction code may be generated or executed in a Physical AI oncology clinical
investigation unless an automated verification, validation, and uncertainty
quantification process, bound to one or more named external standards, has first
cleared for that interaction, and the cleared verification record has been
documented and attested. The full text of subsections (a) through (j) is set out in
section 3 of this Act.}}

\uscprov{1}{\textbf{(c) Section 201(h) (21 U.S.C. 321(h)); Device.}}
\uscquote{0}{``The term `device' means an instrument, apparatus, implement,
machine, ... including any component, part, or accessory,
\cprinsert{including software that generates or executes robot-patient interaction
code in a Physical AI oncology clinical investigation,} which is ... intended to
affect the structure or any function of the body ...''.}

\uscprov{1}{\textbf{(d) Section 301 (21 U.S.C. 331); Prohibited Acts.}}
\uscquote{0}{``The following acts and the causing thereof are prohibited:
\cprinsert{(fff) The generation or execution of robot-patient interaction code in a
Physical AI oncology clinical investigation in violation of section 515D.}''.}

\uscprov{1}{\textbf{(e) Section 501 (21 U.S.C. 351); Adulterated Devices.}}
\uscquote{0}{``A drug or device shall be deemed to be adulterated ...
\cprinsert{(k) if it is a device used in a Physical AI oncology clinical
investigation for which a cleared verification record required by section 515D has
not been documented and attested before the robot-patient interaction code was
generated or executed.}''.}

\uscprov{1}{\textbf{(f) Section 510(k) (21 U.S.C. 360(k)); Premarket Notification.}}
\uscquote{0}{``... a report under this subsection \cprinsert{is not required for a
change to robot-patient interaction code that is governed by, and clears, an
automated verification process consistent with a predetermined change control plan
under section 515C and the verification requirement of section 515D}.''.}

\uscprov{1}{\textbf{(g) Section 520(o) (21 U.S.C. 360j(o)); Clinical Decision
Support.}}
\uscquote{0}{``The term `device' ... shall not include a software function ...
\cprinsert{except that this paragraph does not exclude software that controls or
generates the motion of a robot in direct physical contact with a patient, which
remains a device subject to section 515D}.''.}

\uscprov{1}{\textbf{(h) Section 521 (21 U.S.C. 360k); State and Local
Requirements.}}
\uscquote{0}{``... no State or political subdivision of a State may establish ... any
requirement \cprinsert{except that nothing in this section preempts a State
requirement that preserves a licensed human's authority over an
artificial-intelligence-influenced decision and is not different from, or in
addition to, a requirement under section 515D}.''.}

\uscprov{1}{\textbf{(i) Remaining Conforming Amendments.} Sections 505F (21 U.S.C.
355g), 513 (21 U.S.C. 360c), 515 (21 U.S.C. 360e), and 515C (21 U.S.C. 360e-4) are
amended as described in Table 3 and section 3(b), each by inserting the
section-515D recognition, the graduated special controls, the cleared-record
contents requirement, and the automated verification-before-change protocol,
respectively. No existing text is struck by any conforming amendment; each change is
an insertion, so existing law is preserved in full \cite{usc-355g, usc-360c,
usc-360e, usc-360e4}.}
