% ============================================================
% main.tex
% H. R. 9510 BILL v4.0 - full-bill, single-prompt-bill / auto-bill-01.
%   THE GRAY-SCALE MERMAID AMENDMENT to the Federal Food, Drug, and Cosmetic Act
%   (21 U.S.C. 301 et seq.), grounded on the Title 21 device provisions current
%   through Public Law 119-93.
%
% WHAT THIS FILE IS. This is the finished v4.0 full bill, produced from the
% draft-bill scaffold by executing every bracketed drafting instruction. Every
% gray-scale Mermaid figure is rendered in TikZ and every full-width table is
% filled; the operative text of the amendment is carried so the bill stands on its
% own; and all twelve deliverables are written as LaTeX appendices (Appendix A
% through Appendix L), each listed in the clickable, page-filling table of contents.
% There are no raster images; every diagram is gray-scale.
%
% Compile recipe (Overleaf, pdfLaTeX):
%   pdflatex main.tex
%   bibtex   main
%   pdflatex main.tex
%   pdflatex main.tex
% ============================================================
\documentclass[11pt]{article}
\usepackage{usctitle}

\title{Verification Before Generation in Physical AI Oncology Trials Act of 2026
(H. R. 9510), Bill v4.0: A Gray-Scale Mermaid Amendment to the Federal Food, Drug,
and Cosmetic Act}
\author{Prepared for single-prompt-bill by CEO Kevin Kawchak, ChemicalQDevice}
\date{June 7, 2026 (current through Public Law 119-93)}

\begin{document}

% ============================================================
% BILL CAPTION AND FRONT MATTER (the caption page).
% ============================================================
\thispagestyle{plain}
\pagenumbering{roman}

\billcaption{119TH CONGRESS}{2d Session}{H.\,R. 9510}

\billlongtitle{To amend the Federal Food, Drug, and Cosmetic Act to require an
automated verification, validation, and uncertainty quantification process to
clear robot-patient interaction code before that code is generated or executed in
a Physical AI oncology clinical investigation.}

\billintro{IN THE HOUSE OF REPRESENTATIVES}{June 7, 2026}{%
Mr.\ \underline{Kevin Kawchak} authored the following bill with the assistance of
artificial intelligence; which was referred to the Committee on Energy and
Commerce.}

\billhead

\enactingclause

\billcovernote{\href{https://doi.org/10.5281/zenodo.xxxxxxxx}{Bill (v4.0)
10.5281/zenodo.xxxxxxxx} is the gray-scale Mermaid amendment of H. R. 9510, the
Verification Before Generation in Physical AI Oncology Trials Act of 2026. It
renders nine gray-scale Mermaid figures and eleven full-width tables, carries the
full operative amendment, and writes all twelve submission deliverables as LaTeX
appendices. It was prepared with an autonomous artificial intelligence coding agent
(Claude Code Opus 4.8, 1M context, Max) under human direction. It is an independent
research draft, is not an enacted law, and is not legal advice; the development
record appears in the provenance back matter.}

\begin{mermaidfig}
\node[mmgoal] (mp) at (0,0) {Master prompt (single submission)};
\node[mmstep] (pa) at (-3.4,-1.7) {Process A\\seven sub-prompts};
\node[mmstep] (pb) at (3.4,-1.7) {Process B\\stages 1-7};
\node[mmin]   (dr) at (-4.4,-3.5) {draft-bill\\scaffold};
\node[mmstep] (fu) at (0,-3.5) {full-bill\\(this PDF)};
\node[mmgoal] (fi) at (4.4,-3.5) {final-bill v1.0.0};
\draw[mmedge] (mp) -- (pa);
\draw[mmedge] (mp) -- (pb);
\draw[mmedge] (pa) -- (pb);
\draw[mmedge] (pb) -- (dr);
\draw[mmedge] (pb) -- (fu);
\draw[mmedge] (pb) -- (fi);
\draw[mmedge] (dr) -- (fu);
\draw[mmedge] (fu) -- (fi);
\end{mermaidfig}
\vspace{-0.2cm}
\figcaption{Cover Figure. The Bill v4.0 single-prompt build: one Master prompt
generates every sub-prompt (Process A), which run in sequence (Process B) to grow
the bill from the draft scaffold to this full bill and the polished final bill.}

\clearpage
\pagenumbering{arabic}

% ============================================================
% SECTION 1. SHORT TITLE; TABLE OF CONTENTS.
% ============================================================
\billsec{SECTION 1.}{SHORT TITLE; TABLE OF CONTENTS.}\phantomsection\label{toc:s1}

\uscprov{1}{\textbf{(a) Short Title.} This Act may be cited as the ``Verification
Before Generation in Physical AI Oncology Trials Act of 2026''.}

\uscprov{1}{\textbf{(b) Table of Contents.} The table of contents for this Act
version is as follows. Each entry links to the part it names.}

\vspace{0.4\baselineskip}
\billtoc{%
\billtocline{toc:s1}{Sec.~1.}{Short title; table of contents.}{The citation and
this clickable contents.}
\vfill
\billtocline{toc:s2}{Sec.~2.}{Findings; the evidence to law record.}{Why the
rule is needed and feasible, with the four-work record.}
\vfill
\billtocline{toc:s3}{Sec.~3.}{Amendment to the Federal Food, Drug, and Cosmetic
Act.}{New section 515D and ten conforming amendments.}
\vfill
\billtocline{toc:s4}{Sec.~4.}{Comparative print; changes in existing law.}{The
eleven affected Title 21 device sections, marked.}
\vfill
\billtocline{toc:aA}{App.~A.}{One-page summary.}{The problem, the rule, the
evidence, and the ask, on one page.}
\vfill
\billtocline{toc:aB}{App.~B.}{Section-by-section analysis.}{Plain-English gloss of
every operative part.}
\vfill
\billtocline{toc:aC}{App.~C.}{Plain-English policy memo.}{Why the sequencing gap
matters and why the gate fits existing law.}
\vfill
\billtocline{toc:aD}{App.~D.}{Legislative findings.}{The fourteen findings of fact,
each tied to an in-force authority.}
\vfill
\billtocline{toc:aE}{App.~E.}{Ramseyer comparative print.}{Changes to existing law,
marked, for the affected sections.}
\vfill
\billtocline{toc:aF}{App.~F.}{Constitutional Authority Statement.}{The Commerce
Clause basis (House Rule XII).}
\vfill
\billtocline{toc:aG}{App.~G.}{PAYGO and cost estimate.}{PAYGO note and a negative
earmark declaration.}
\vfill
\billtocline{toc:aH}{App.~H.}{Sponsor and cosponsor packet.}{The sponsor role and
the cosponsor form.}
\vfill
\billtocline{toc:aI}{App.~I.}{Stakeholder engagement plan.}{Outreach to agencies,
advocacy, industry, and standards bodies.}
\vfill
\billtocline{toc:aJ}{App.~J.}{Legislative Counsel routing memo.}{The
legislative-form questions for HOLC.}
\vfill
\billtocline{toc:aK}{App.~K.}{Currency and cross-reference matrix.}{Re-verification
that every citation still lands.}
\vfill
\billtocline{toc:aL}{App.~L.}{Testimony and research-influence brief.}{Hearing
testimony; emerging bills kept out of the text.}
}

\clearpage

% ============================================================
% BILL BODY AND APPENDICES (one file per section; each corresponds to main.tex).
% ============================================================
\input{sections/s2-findings}
\input{sections/s3-amendment}
\input{sections/s4-comparative}
\input{sections/a-one-page-summary}
\input{sections/b-section-by-section}
\input{sections/c-policy-memo}
\input{sections/d-findings}
\input{sections/e-ramseyer}
\input{sections/f-constitutional-authority}
\input{sections/g-paygo-cost}
\input{sections/h-sponsor-cosponsor}
\input{sections/i-stakeholder}
\input{sections/j-counsel-routing}
\input{sections/k-currency-matrix}
\input{sections/l-testimony-influence}

% ============================================================
% AUTHORSHIP, NOTICES, AND PROVENANCE.
% ============================================================
\clearpage
\vspace{0.3cm}
\phantomsection
\addcontentsline{toc}{section}{Authorship, Notices, and Provenance}
\usccrosshead{AUTHORSHIP, NOTICES, AND PROVENANCE}

\uscnotepar{Prepared by CEO Kevin Kawchak
(\href{https://orcid.org/0009-0007-5457-8667}{ORCID 0009-0007-5457-8667}),
ChemicalQDevice (\href{mailto:kevink@chemicalqdevice.com}{kevink@chemicalqdevice.com}).
Adapted using Claude Code Opus 4.8 (1M context) Max; research assisted by ChatGPT
and Google Gemini.}

\uscnotepar{Notice: This measure was adapted from documents of the United States
Government in the public domain under 17 U.S.C. 105. The reproduced statutory text
is in the public domain; the authoritative version is the United States Code as
published by the Office of the Law Revision Counsel. This work is not endorsed or
sponsored by the FDA, HHS, the OLRC, CFR, ICH, or any member of Congress.}

\uscnotepar{Disclaimer: This work is an independent research draft, is not an
enacted law, and is not legal advice; it is not endorsed, sponsored, or approved by
any trial sponsor, contract research organization, site, institutional review
board, regulator, or medical society. All supporting numbers are simulation or
illustrative results from the seed 20260525, and no patient-identifiable
information is included.}

\uscnotepar{Rights: The reproduced statutory text is in the public domain; the
generated amendment framing, figures, tables, and notices are released under the
Creative Commons Attribution 4.0 International License (CC BY 4.0),
\href{https://creativecommons.org/licenses/by/4.0/}{https://creativecommons.org/licenses/by/4.0/}.}

\href{https://doi.org/10.5281/zenodo.xxxxxxxx}{DOI current bill (v4.0): 10.5281/zenodo.xxxxxxxx}

\href{https://doi.org/10.5281/zenodo.xxxxxxxx}{DOI prior bill (v3.0): 10.5281/zenodo.xxxxxxxx}

\href{https://doi.org/10.5281/zenodo.xxxxxxxx}{DOI repository: 10.5281/zenodo.xxxxxxxx}

\uscnotepar{San Diego. June 7, 2026.}

% ============================================================
% PROVENANCE AND RESEARCH SOURCES (BIBLIOGRAPHY).
% ============================================================
\clearpage
\phantomsection
\addcontentsline{toc}{section}{Provenance and Research Sources}
\usccrosshead{Provenance and Research Sources}
\vspace{-0.4cm}

\begingroup
\RaggedRight
\nocite{*}
\bibliographystyle{ieeetr}
\bibliography{references}
\endgroup

\end{document}
