% ============================================================
% main.tex
% H. R. 9510 BILL v5.0 - draft-bill (scaffold), single-prompt-bill / auto-bill-02.
%   THE FINANCIAL DATA AMENDMENT to the Federal Food, Drug, and Cosmetic Act
%   (21 U.S.C. 301 et seq.), grounded on the Title 21 device provisions current
%   through Public Law 119-93.
%
% WHAT THIS FILE IS. This is the Bill v5.0 draft scaffold. It lays out the full
% congressional amendment structure (caption; A BILL; enacting clause; SECTION 1
% short title and a clickable, page-filling table of contents; SEC. 2 findings as
% the evidence-to-law-to-cost record; SEC. 3 the operative amendment with the new
% financial-data record; SEC. 4 the comparative print widened to the user-fee
% section; SEC. 5 the financial core - transparency, user fees, authorization of
% appropriations, budgetary effects) and, for the five financial appendices
% (A through E), bracketed [DRAFTING INSTRUCTIONS] that name the exact upstream
% files to process and the figure or table medium each slot carries. The full
% bill executes every instruction; this scaffold compiles as committed.
%
% Media (Master prompt objective (b)): full-width white-background tables;
% centered monospace ASCII figures (asciifig); gray-scale Mermaid diagrams
% reproduced as gray-scale TikZ (mermaidfig). No raster images anywhere.
%
% Compile recipe (Overleaf, pdfLaTeX):
%   pdflatex main.tex
%   bibtex   main
%   pdflatex main.tex
%   pdflatex main.tex
% ============================================================
\documentclass[11pt]{article}
\usepackage{usctitle}

\title{Verification Before Generation in Physical AI Oncology Trials Act of 2026
(H. R. 9510), Bill v5.0: A Financial Data Amendment to the Federal Food, Drug,
and Cosmetic Act}
\author{Prepared for single-prompt-bill by CEO Kevin Kawchak, ChemicalQDevice}
\date{June 9, 2026 (current through Public Law 119-93)}

\begin{document}

% ============================================================
% BILL CAPTION AND FRONT MATTER (the caption page). The House and Senate
% statements are condensed: the long title appears once, the referral block is
% brief, and the standard enacting clause is retained. A centered ASCII overview
% of the v5.0 financial build closes the page.
% ============================================================
\thispagestyle{plain}
\pagenumbering{roman}

\billcaption{119TH CONGRESS}{2d Session}{H.\,R. 9510}

\billlongtitle{To amend the Federal Food, Drug, and Cosmetic Act to require an
automated verification, validation, and uncertainty quantification process to
clear robot-patient interaction code before that code is generated or executed
in a Physical AI oncology clinical investigation, to establish financial data
transparency for that process, and to authorize appropriations.}

\billintro{IN THE HOUSE OF REPRESENTATIVES}{June 9, 2026}{%
Mr.\ \underline{Kevin Kawchak} authored the following bill with the assistance of
artificial intelligence; which was referred to the Committee on Energy and
Commerce.}

\billhead

\enactingclause

\billcovernote{\href{https://doi.org/10.5281/zenodo.xxxxxxxx}{Bill (v5.0)
10.5281/zenodo.xxxxxxxx} is the Financial Data Amendment of H. R. 9510, the
Verification Before Generation in Physical AI Oncology Trials Act of 2026. It
carries the full operative amendment with a new financial-data record, a
financial core (transparency, user fees, an authorization of appropriations,
and the budgetary-effects clause), and five financial appendices, rendered in
three media: full-width tables, centered ASCII figures, and gray-scale Mermaid
diagrams set as TikZ. It was prepared with an autonomous artificial
intelligence coding agent (Claude Code, 1M context) under human direction. It
is an independent research draft, is not an enacted law, and is not legal
advice; all dollar figures are illustrative unless tied to a cited statute or
notice. The development record appears in Appendix E.}

\begin{asciifig}
EVIDENCE + LAW (v1.0 - v4.0)                 FINANCIAL FRAME (2026)
+----------------------------------+         +----------------------------------+
| VVUQ-01/02  method + hard proof  |         | PAYGO 2 U.S.C. 931-939           |
| VVUQ-03/04  bill + FD&C 515D     |  =====> | CutGo House Rule XXI cl. 10      |
| v3.0 visual  v4.0 Mermaid        |         | MDUFA V fees 21 U.S.C. 379i-379j |
+----------------------------------+         | part 54 + Open Payments          |
                 |                           +----------------------------------+
                 v                                            |
        single-prompt-bill/auto-bill-02  (this build)         |
        +--------------------------------------------------+  |
        | sub-prompts -> research -> template -> visuals   |<-+
        | -> draft-bill -> full-bill -> final-bill v2.0.0  |
        +--------------------------------------------------+
                 |
                 v
        H. R. 9510 BILL v5.0  <== THE FINANCIAL DATA AMENDMENT
        cost records (515D(k)) + SEC. 5 transparency, user fees,
        authorization of appropriations, budgetary effects
\end{asciifig}
\vspace{-0.4cm}
\figcaption{Cover Figure. The Bill v5.0 financial build: the evidence-to-law
record of the four prior versions, read against the 2026 financial frame and
reorganized through this build into the Financial Data Amendment.}

\clearpage
\pagenumbering{arabic}

% ============================================================
% SECTION 1. SHORT TITLE; TABLE OF CONTENTS.
% The table of contents is clickable (each entry links to its part) and is set
% to fill the remainder of the page with evenly distributed entries.
% ============================================================
\billsec{SECTION 1.}{SHORT TITLE; TABLE OF CONTENTS.}\phantomsection\label{toc:s1}

\uscprov{1}{\textbf{(a) Short Title.} This Act may be cited as the
``Verification Before Generation in Physical AI Oncology Trials Act of 2026''.}

\uscprov{1}{\textbf{(b) Table of Contents.} The table of contents for this Act
version is as follows. Each entry links to the part it names.}

\vspace{0.4\baselineskip}
\billtoc{%
\billtocline{toc:s1}{Sec.~1.}{Short title; table of contents.}{The citation and
this clickable contents.}
\vfill
\billtocline{toc:s2}{Sec.~2.}{Findings; the evidence to law to cost record.}{Why
the rule is needed and feasible, and what the record cost to produce.}
\vfill
\billtocline{toc:s3}{Sec.~3.}{Amendment to the Federal Food, Drug, and Cosmetic
Act.}{New section 515D with the financial-data record, and ten conforming
amendments.}
\vfill
\billtocline{toc:s4}{Sec.~4.}{Comparative print; changes in existing law.}{The
twelve affected Title 21 sections, including the user-fee section, marked.}
\vfill
\billtocline{toc:s5}{Sec.~5.}{Financial data transparency; user fees;
authorization of appropriations; budgetary effects.}{The operative financial
core of the v5.0 amendment.}
\vfill
\billtocline{toc:a6}{App.~A.}{Cost estimate and budgetary data
(non-operative).}{The pre-introduction estimate: budget authority, outlays,
fees, scorecards, mandates.}
\vfill
\billtocline{toc:a7}{App.~B.}{Verification economics and financial evidence
(non-operative).}{What the four-work record says a verification run costs.}
\vfill
\billtocline{toc:a8}{App.~C.}{The financial-data transparency standard
(non-operative).}{Completeness, traceability, periodicity, comparability,
mapped to in-force instruments.}
\vfill
\billtocline{toc:a9}{App.~D.}{Research influence matrix, financial
(non-operative).}{Emerging financial bills and actions, kept out of the
operative text.}
\vfill
\billtocline{toc:a10}{App.~E.}{Development transparency and commit
schedule.}{How Bill v5.0 was built across nine real-time milestones.}
}

\clearpage

% ============================================================
% BILL BODY AND APPENDICES (one file per section; each corresponds to main.tex).
% The bill body (SEC. 2 through SEC. 5) carries the operative text and the
% rendered financial visuals; the appendices carry the cost estimate, the
% verification economics, the financial-data standard, the influence matrix,
% and the transparency record.
% ============================================================
\input{sections/s2-findings}
\input{sections/s3-amendment}
\input{sections/s4-comparative}
\input{sections/s5-financial}
\input{sections/a6-cost-estimate}
\input{sections/a7-verification-economics}
\input{sections/a8-financial-standard}
\input{sections/a9-research-matrix}
\input{sections/a10-transparency}

% ============================================================
% AUTHORSHIP, NOTICES, AND PROVENANCE.
% ============================================================
\clearpage
\vspace{0.3cm}
\phantomsection
\addcontentsline{toc}{section}{Authorship, Notices, and Provenance}
\usccrosshead{AUTHORSHIP, NOTICES, AND PROVENANCE}

\uscnotepar{Prepared by CEO Kevin Kawchak
(\href{https://orcid.org/0009-0007-5457-8667}{ORCID 0009-0007-5457-8667}),
ChemicalQDevice (\href{mailto:kevink@chemicalqdevice.com}{kevink@chemicalqdevice.com}).
Adapted using an autonomous Claude Code agent (Anthropic, 1M context); research
assisted by ChatGPT and Google Gemini.}

\uscnotepar{Notice: This measure was adapted from documents of the United States
Government in the public domain under 17 U.S.C. 105. The reproduced statutory
text is in the public domain; the authoritative version is the United States
Code as published by the Office of the Law Revision Counsel. This work is not
endorsed or sponsored by the FDA, HHS, the CBO, the GAO, the OMB, the OLRC, CFR,
ICH, or any member of Congress.}

\uscnotepar{Disclaimer: This work is an independent research draft, is not an
enacted law, and is not legal advice; it is not endorsed, sponsored, or approved
by any trial sponsor, contract research organization, site, institutional review
board, regulator, or medical society. All supporting numbers, including every
dollar figure not tied to a cited statute or published notice, are simulation
or illustrative results from the seed 20260525, and no patient-identifiable
information is included. No formal Congressional Budget Office estimate exists
for this draft.}

\uscnotepar{Rights: The reproduced statutory text is in the public domain; the
generated amendment framing, figures, tables, and notices are released under the
Creative Commons Attribution 4.0 International License (CC BY 4.0),
\href{https://creativecommons.org/licenses/by/4.0/}{https://creativecommons.org/licenses/by/4.0/}.}

\href{https://doi.org/10.5281/zenodo.xxxxxxxx}{DOI current bill (v5.0): 10.5281/zenodo.xxxxxxxx}

\href{https://doi.org/10.5281/zenodo.20576907}{DOI prior bill (v4.0): 10.5281/zenodo.20576907}

\href{https://doi.org/10.5281/zenodo.20535429}{DOI prior bill (v3.0): 10.5281/zenodo.20535429}

\href{https://doi.org/10.5281/zenodo.20576648}{DOI repository: 10.5281/zenodo.20576648}

\uscnotepar{San Diego. June 9, 2026.}

% ============================================================
% PROVENANCE AND RESEARCH SOURCES (BIBLIOGRAPHY).
% A real congressional bill carries no bibliography; this research-aid back
% matter does, so the operative text stays clean while sources remain auditable.
% ============================================================
\clearpage
\phantomsection
\addcontentsline{toc}{section}{Provenance and Research Sources}
\usccrosshead{Provenance and Research Sources}
\vspace{-0.6cm}

\begingroup
\RaggedRight
\nocite{*}
\bibliographystyle{ieeetr}
\bibliography{references}
\endgroup

\end{document}
