%% ============================================================
%% sections/a9-research-matrix.tex
%% H. R. 9510 Bill v5.0 - APPENDIX D. RESEARCH INFLUENCE MATRIX, FINANCIAL
%% (NON-OPERATIVE). Emerging financial bills, the reauthorization timetable,
%% and executive actions, kept out of the operative text.
%% Rendered visual: Table 13 (the financial research-influence matrix). A
%% matrix is a table; no diagram belongs in this appendix.
%% ============================================================
\phantomsection\label{toc:a9}
\addcontentsline{toc}{section}{Appendix D. Research Influence Matrix, Financial (Non-Operative)}
\usccrosshead{APPENDIX D. RESEARCH INFLUENCE MATRIX, FINANCIAL (NON-OPERATIVE)}

\uscprov{1}{The authorities in this appendix are research influences only.
They inform the financial findings, the cost appendix, and this matrix, but
none is cited as the legal basis of an operative clause of this Act. Only
enacted statutes, in-force rules, and recognized instruments carry operative
weight, so the emerging financial bills, the reauthorization timetable, and
the executive actions are kept here and out of the bill text, consistent with
the operative-versus-influence rule the prior bills follow
\cite{kawchak2026vvuq04bill}. Each entry is verified by number, subject, and
status before use.}

{\footnotesize
\begin{xltabular}{\textwidth}{@{}L{2.4cm} L{4.2cm} Y L{2.2cm}@{}}
\hline\noalign{\vskip 0.04cm}
\textbf{Authority} & \textbf{What it is} & \textbf{What it informs} &
\textbf{Placement}\\
\hline\noalign{\vskip 0.04cm}
\endfirsthead
\hline\noalign{\vskip 0.04cm}
\textbf{Authority} & \textbf{What it is} & \textbf{What it informs} &
\textbf{Placement}\\
\hline\noalign{\vskip 0.04cm}
\endhead
\hline\noalign{\vskip 0.04cm}
\endlastfoot
MDUFA VI window & Device user-fee authority expires with fiscal year 2027; the
successor must be enacted before October 1, 2027 \cite{pl-mdufa5} & The SEC.
5(c)(2) sense of Congress: price verification workload there & SEC. 5(c)(2);
matrix\\
\hline\noalign{\vskip 0.04cm}
Annual fee notices & Federal Register notices setting each year's device
user-fee dollar amounts \cite{fda-mdufa-rates} & Why Table 8 carries statutory
percentages, not dollars & App. A; matrix\\
\hline\noalign{\vskip 0.04cm}
FDA S\&E climate & The annual agriculture appropriations cycle funding the
Salaries and Expenses account & The Table 6 activity profile and outlay
assumptions & App. A; matrix\\
\hline\noalign{\vskip 0.04cm}
S. 1399 & Health Tech Investment Act; a Medicare payment class for
algorithm-based services \cite{s1399-health-tech-investment} & Coverage
economics direction in the findings narrative & Findings narr.; matrix\\
\hline\noalign{\vskip 0.04cm}
H.R. 6361 & Ban AI Denials in Medicare Act \cite{hr6361-ban-ai-denials} &
Human-over-AI cost signal & Findings narr.; matrix\\
\hline\noalign{\vskip 0.04cm}
H.R. 5045 & HEALTH AI Act; an HHS generative-AI grant program
\cite{hr5045-health-ai} & Federal funding-stream direction & Matrix\\
\hline\noalign{\vskip 0.04cm}
EO 14179 & Removing Barriers to American Leadership in AI (90 FR 8741)
\cite{eo-14179} & Deregulatory posture the cost appendix prices against &
App. A narr.; matrix\\
\hline\noalign{\vskip 0.04cm}
OMB M-25-21 & Accelerating Federal Use of AI \cite{omb-m2521} &
Pre-deployment testing cost analogue & Matrix\\
\hline\noalign{\vskip 0.04cm}
HHS AI Strategy & The December 2025 HHS strategy \cite{hhs-ai-strategy-2025} &
Governance and reproducibility framing for the records system & Matrix\\
\hline
\end{xltabular}}
\vspace{-0.8cm}
\figcaption{Table 13. The financial research-influence matrix: each authority,
what it is, what it informs in the bill package, and its placement. No row is
cited from an operative clause; the operative sections and the comparative
print remain free of these authorities.}

\uscprov{1}{The placement column is the discipline: an influence may shape a
finding's narrative, an appendix assumption, or a sense of Congress, and
nothing more. The single timing fact with operative adjacency - the MDUFA VI
window - enters the operative text only as a sense of Congress in section
5(c)(2), which binds no one \cite{pl-mdufa5}.}
