%% ============================================================
%% sections/a10-transparency.tex - H. R. 9510 Bill v5.0 (draft scaffold)
%% APPENDIX E. DEVELOPMENT TRANSPARENCY AND COMMIT SCHEDULE.
%% Planned visuals: Table 14 (bill version lineage v1.0-v5.0), Table 15 (the
%% nine-milestone commit schedule), Figure 11 (Mermaid build process, TikZ).
%% ============================================================
\phantomsection\label{toc:a10}
\addcontentsline{toc}{section}{Appendix E. Development Transparency and Commit Schedule}
\usccrosshead{APPENDIX E. DEVELOPMENT TRANSPARENCY AND COMMIT SCHEDULE}

\uscprov{1}{\textbf{What was built, and how.} Bill v5.0 (repository release
v2.0.0) is the Financial Data Amendment of H. R. 9510. It was produced by an
autonomous artificial intelligence coding agent (Claude Code, 1M context)
operating under human direction in a managed, ephemeral cloud container, from
a single Master prompt: Process A generated seven sub-prompts, and Process B
ran them in sequence through four research stages and three bill stages. It
was authored across sequential commits, one file per commit pushed to GitHub
in real time, with the nine stage milestones tracked in one continuously
updated pull request on the single permitted branch. Only
kevinkawchak/single-prompt-bill was edited \cite{anthropic-claude-code,
repo-single-prompt-bill}.}

\uscprov{0}{[DRAFTING INSTRUCTIONS - APPENDIX E. Render Table 14 (the bill
version lineage: v1.0 VVUQ-03, v2.0 VVUQ-04, v3.0 VVUQ-05, v4.0 auto-bill-01
with DOI 10.5281/zenodo.20576907, v5.0 this measure with the Rule 15
placeholder DOI); Table 15 (the nine-milestone commit schedule of this build:
M1 bootstrap and the PR, M2-M5 the research stages, M6-M8 the bill stages
with one commit per .tex/.md/.zip, M9 the release update); and Figure 11
(the gray-scale Mermaid nine-milestone build flowchart from Stage 3, as
TikZ). Close with how the measure is implemented as law (the 365-day
rulemaking, the effective date, the 180-day transition) extended by the v5.0
financial implementation facts (the first annual financial-data summaries;
the MDUFA VI pricing window; the appropriations sequence from Table 6), and
note that the financial-data standard of Appendix C grades this appendix's
own commit record. \cite{kawchak2026autobill01}]}

\uscprov{1}{[TABLE 14 SLOT - version lineage. TABLE 15 SLOT - milestone commit
schedule. FIGURE 11 SLOT - Mermaid build process. Each is rendered in the
full bill.]}
