%% ============================================================
%% sections/a7-verification-economics.tex - H. R. 9510 Bill v5.0 (draft scaffold)
%% APPENDIX B. VERIFICATION ECONOMICS AND FINANCIAL EVIDENCE (NON-OPERATIVE).
%% Planned visuals: Figure 9 (Mermaid clustered component, unit economics,
%% TikZ), Table 10 (per-gate unit-cost schedule), Table 11 (acceleration
%% economics summary).
%% ============================================================
\clearpage
\phantomsection\label{toc:a7}
\addcontentsline{toc}{section}{Appendix B. Verification Economics and Financial Evidence (Non-Operative)}
\usccrosshead{APPENDIX B. VERIFICATION ECONOMICS AND FINANCIAL EVIDENCE (NON-OPERATIVE)}

\uscprov{1}{This appendix is non-operative. It reads the VVUQ-01 and VVUQ-02
engineering record as a ledger: what one ten-gate verification run costs, how
that unit cost scales over an investigation, and what the four-work record
implies about the cost of the conventional path the gate replaces. None of
these figures is cited as the legal basis of an operative clause; all are
illustrative or simulation results from the seed 20260525
\cite{kawchak2026vvuq01, kawchak2026vvuq02}.}

\uscprov{0}{[DRAFTING INSTRUCTIONS - APPENDIX B. Build the economics from the
four-work record (51 of 51 tests; 172 of 172 tests; 10 gates; 32 of 32 sweep
iterations; about eleven days of autonomous work) priced at illustrative
compute, storage, and review rates. Render Figure 9 (the gray-scale Mermaid
clustered-component unit-economics pipeline from Stage 3, as TikZ); Table 10
(the per-gate unit-cost schedule: illustrative compute cost per run for each
of the ten gates, an R column, with the three hard-predicate gates carrying
the added catastrophe-simulation cost, plus records and review lines, summing
to the cost per cleared interaction class); and Table 11 (the acceleration
economics summary: the conventional program-year ledger beside the autonomous
record, consistent with Figure 2 in SEC. 2). Tie each row back to the
recorded evidence so every dollar is traceable to a test count or a release
range (the Appendix C traceability test).]}

\uscprov{1}{[FIGURE 9 SLOT - Mermaid unit-economics pipeline. TABLE 10 SLOT -
per-gate unit costs. TABLE 11 SLOT - acceleration economics. Each is rendered
in the full bill.]}
