%% ============================================================
%% sections/s2-findings.tex - H. R. 9510 Bill v5.0 (draft scaffold)
%% SEC. 2. FINDINGS; THE EVIDENCE TO LAW TO COST RECORD.
%% Planned visuals: Figure 1 (Mermaid lineage, TikZ), Table 1 (four works with
%% the financial footprint), Figure 2 (ASCII cost ledger).
%% ============================================================
\billsec{SEC. 2.}{FINDINGS; THE EVIDENCE TO LAW TO COST RECORD.}\phantomsection\label{toc:s2}

\uscprov{1}{\textbf{(a) In General.} Congress finds that an automated process
must verify robot-patient interaction code before that code is generated or
executed in a Physical AI oncology clinical investigation; that the VVUQ-01
through VVUQ-04 record establishes the need for and feasibility of that
requirement; and that the same record, read as a ledger, shows the requirement
is affordable: the verification data that proves safety is financial data the
moment a cost is attached to each run \cite{kawchak2026national,
kawchak2026vvuq01, kawchak2026vvuq02}.}

\uscprov{0}{[DRAFTING INSTRUCTIONS - SEC. 2. Carry the findings of
\texttt{cancer-automated/.../VVUQ-05/final-bill/sections/s2-findings.tex}
(the embodiment problem and sequencing gap; demonstrated feasibility; the
closest existing analogues; the recognized standards basis; the State
human-over-AI adoption; modernization and nondiscrimination), condensed, and
ADD the v5.0 financial findings from
\texttt{auto-bill-02/01-research/output-1-research.md}: (b) the financial-data
gap - no Federal law prices or discloses the cost of verifying robot-patient
interaction code, although part 54 of title 21, Code of Federal Regulations,
and the Open Payments system already make adjacent clinical-trial money
flows reportable; (c) the cost asymmetry - an embodied failure is priced in
lives and litigation while an automated ex ante gate is priced in compute;
(d) the affordability finding from the four-work ledger; and (e) the budget
discipline finding - the requirement rides existing appropriations and the
MDUFA fee structure without new direct spending. Render Figure 1 (gray-scale
Mermaid flowchart LR, evidence-to-law-to-cost lineage, as TikZ), Table 1 (the
four works at a glance WITH the illustrative financial footprint column, the
R column right-aligned), and Figure 2 (ASCII side-by-side cost ledger from
Stage 3, all figures illustrative, seed 20260525).]}

\uscprov{1}{[FIGURE 1 SLOT - Mermaid lineage. TABLE 1 SLOT - four works with
financial footprint. FIGURE 2 SLOT - ASCII cost ledger. Each is rendered in
the full bill.]}
