%% ============================================================
%% sections/s3-amendment.tex - H. R. 9510 Bill v5.0 (draft scaffold)
%% SEC. 3. AMENDMENT TO THE FEDERAL FOOD, DRUG, AND COSMETIC ACT.
%% Planned visuals: Table 2 (ten-gate schedule with unit costs), Figure 3
%% (Mermaid BPMN decision rule with the cost-record checkpoint, TikZ),
%% Figure 4 (ASCII statutory layering with the financial sections), Table 3
%% (ten conforming amendments crosswalk).
%% ============================================================
\billsec{SEC. 3.}{AMENDMENT TO THE FEDERAL FOOD, DRUG, AND COSMETIC ACT.}\phantomsection\label{toc:s3}

\uscprov{1}{\textbf{(a) In General.} Subchapter V of the Federal Food, Drug, and
Cosmetic Act (21 U.S.C. 351 et seq.) is amended by inserting after section 515C
(21 U.S.C. 360e-4) a new section 515D (21 U.S.C. 360e-5) requiring verification
before generation of robot-patient interaction code, and - new in this version -
requiring that a financial-data record (the direct cost of each verification
run) be written to the same hash-chained audit trail the section already
demands.}

\uscprov{0}{[DRAFTING INSTRUCTIONS - SEC. 3. Carry the full operative new
section 515D from
\texttt{cancer-automated/.../VVUQ-05/final-bill/sections/s3-amendment.tex}
(subsections (a) Requirement through (j) Rule of Construction) so the bill
stands on its own, and ADD new subsection (k) Financial Data Record: for each
verification run, the sponsor records the direct cost (compute, records
storage, and any human review on an ESCALATE), aggregated per gate and per
interaction class, in the part 11 audit trail; the record is attested with the
compliance statement under subsection (e); and the sponsor reports the annual
aggregate to the Secretary under section 5 of this Act. Renumber the carried
definitions and rule-of-construction subsections accordingly ((i) Definitions
adds the terms `verification cost record' and `direct cost'; the carried (k)
Rule of Construction becomes (l)). Then carry the ten conforming amendments,
the clerical amendment, the rule of construction, and the effective date
verbatim. Render Table 2 (the ten-gate threshold schedule EXTENDED by one
illustrative unit-cost-per-run R column, seed 20260525), Figure 3 (gray-scale
Mermaid BPMN decision rule with the new cost-record checkpoint on the ACCEPT
path, as TikZ, from Stage 3), Figure 4 (ASCII statutory layering extended to
the financial sections - 379i/379j, 351, 331, 355g, 360k - from Stage 3), and
Table 3 (the ten conforming amendments crosswalk, carried). Use the section
symbol for every codified reference; single hyphens only.]}

\uscprov{1}{[TABLE 2 SLOT - gate schedule with unit costs. FIGURE 3 SLOT -
decision rule with cost-record checkpoint. FIGURE 4 SLOT - financial statutory
layering. TABLE 3 SLOT - conforming crosswalk. Each is rendered in the full
bill.]}
