%% ============================================================
%% sections/s4-comparative.tex - H. R. 9510 Bill v5.0 (draft scaffold)
%% SEC. 4. COMPARATIVE PRINT; CHANGES IN EXISTING LAW.
%% Planned visuals: Table 4 (twelve-section change map), Figure 5 (ASCII
%% comparative-print order), then the reproduced provisions.
%% ============================================================
\billsec{SEC. 4.}{COMPARATIVE PRINT; CHANGES IN EXISTING LAW.}\phantomsection\label{toc:s4}

\uscprov{1}{The following comparative print shows the changes proposed to
existing law by this Act. Matter proposed to be deleted is shown as
\cprstrike{matter to be deleted}; matter proposed to be inserted is shown as
\cprinsert{matter to be inserted}; existing law in which no change is proposed
is shown as regular text, and unchanged matter omitted for brevity is shown by
a row of asterisks \cite{usc-fdca, olrc-usc21}.}

\uscprov{0}{[DRAFTING INSTRUCTIONS - SEC. 4. Carry the eleven reproduced Title
21 device sections of
\texttt{cancer-automated/.../VVUQ-05/final-bill/sections/s4-comparative.tex}
verbatim (s301, s321, s331, s351, s355g, s360, s360c, s360e, s360e-4, s360j,
s360k, each showing only its affected matter with insertions and deletions
marked and omitted matter as a row of asterisks), and ADD a twelfth reproduced
section: \S~379j (FD\&C Act \S~738, authority to assess and use device fees),
with the v5.0 insertion made by SEC. 5(c) of this Act - the filing of a
verification record under section 515D, alone, is not a fee-bearing
submission. Render Table 4 (the per-section change map, now twelve rows
including s379j) and Figure 5 (the ASCII comparative-print order from Stage 3,
twelve sections in 21 U.S.C. order). Keep the print current through Public Law
119-93 \cite{pl-119-93}.]}

\uscprov{1}{[TABLE 4 SLOT - twelve-section change map. FIGURE 5 SLOT - ASCII
print order. The twelve reproduced provisions follow in the full bill.]}
