%% ============================================================
%% sections/s5-financial.tex - H. R. 9510 Bill v5.0 (draft scaffold)
%% SEC. 5. FINANCIAL DATA TRANSPARENCY; USER FEES; AUTHORIZATION OF
%% APPROPRIATIONS; BUDGETARY EFFECTS. The operative financial core, NEW in
%% v5.0. Planned visuals: Table 5 (financial-data elements dictionary),
%% Figure 6 (Mermaid sequence, annual reporting flow, TikZ), Table 6
%% (authorization schedule), Figure 7 (ASCII money flow), and the boxed
%% budgetary-effects clause (billbox).
%% ============================================================
\billsec{SEC. 5.}{FINANCIAL DATA TRANSPARENCY; USER FEES; AUTHORIZATION OF
APPROPRIATIONS; BUDGETARY EFFECTS.}\phantomsection\label{toc:s5}

\uscprov{1}{\textbf{(a) Financial Data Transparency.} The Secretary shall
publish, annually and in de-identified aggregate form, the verification cost
records reported under section 515D(k) of the Federal Food, Drug, and Cosmetic
Act, in the manner of the transparency reports under section 1128G of the
Social Security Act (42 U.S.C. 1320a-7h), with no patient-identifiable and no
proprietary line-item information.}

\uscprov{0}{[DRAFTING INSTRUCTIONS - SEC. 5. Draft the four operative
financial subsections in full from
\texttt{auto-bill-02/01-research/output-1-research.md}: (a) the annual
de-identified publication duty above, with the financial-data elements
dictionary in Table 5; (b) Financial Disclosure Alignment - clinical
investigators' part 54 disclosure discipline (21 CFR part 54, Forms FDA 3454
and 3455) applies to financial arrangements between sponsors and
verification-service providers; (c) User-Fee Treatment - amend \S~738 (21
U.S.C. 379j) so a verification record filed under section 515D, alone, is not
a fee-bearing submission, and direct that any verification-review workload be
priced in the next user-fee reauthorization (MDUFA VI, due before October 1,
2027) rather than by a new statutory fee; (d) Authorization of Appropriations
- such sums as set out in Table 6 (illustrative: 18, 12, 10, 9, and 9 million
dollars for fiscal years 2027 through 2031, totaling 58 million dollars) for
rulemaking under section 515D(h), the verification-records system, sequencing
inspections, and the annual summaries, to remain available until expended,
with the GAO vocabulary used exactly (authorized to be appropriated, not
appropriated); and (e) Budgetary Effects - the standard Statutory PAYGO
clause, set in the billbox device. Render Figure 6 (gray-scale Mermaid
sequence diagram, the annual reporting flow sponsor to audit trail to
Secretary to public summary to Congress, as TikZ) and Figure 7 (the ASCII
money-flow map from Stage 3). Cite \S~379i-\S~379j, the Statutory PAYGO Act,
and House Rule XXI in the research-aid notes only \cite{usc-379j,
usc-paygo-2010, house-rule-xxi, cfr-part54, usc-open-payments}.]}

\uscprov{1}{[TABLE 5 SLOT - financial-data elements dictionary. FIGURE 6 SLOT -
Mermaid reporting sequence. TABLE 6 SLOT - authorization schedule. FIGURE 7
SLOT - ASCII money flow. BILLBOX SLOT - budgetary-effects clause. Each is
rendered in the full bill.]}
