%% ============================================================
%% sections/a7-verification-economics.tex
%% H. R. 9510 Bill v5.0 - APPENDIX B. VERIFICATION ECONOMICS AND FINANCIAL
%% EVIDENCE (NON-OPERATIVE). The VVUQ-01/02 record read as a ledger.
%% Rendered visuals: Figure 9 (Mermaid clustered component, unit economics,
%% TikZ), Table 10 (per-gate unit-cost schedule), Table 11 (acceleration
%% economics summary).
%% ============================================================
\clearpage
\phantomsection\label{toc:a7}
\addcontentsline{toc}{section}{Appendix B. Verification Economics and Financial Evidence (Non-Operative)}
\usccrosshead{APPENDIX B. VERIFICATION ECONOMICS AND FINANCIAL EVIDENCE (NON-OPERATIVE)}

\uscprov{1}{This appendix is non-operative. It reads the VVUQ-01 and VVUQ-02
engineering record as a ledger: what one ten-gate verification run costs, how
the unit cost composes into the cost per cleared interaction class, and how
that compares with the conventional path the gate replaces. None of these
figures is cited as the legal basis of an operative clause; all are
illustrative or simulation results from the seed 20260525, and each row is
traceable to a recorded test count or release range - the traceability test
of Appendix C \cite{kawchak2026vvuq01, kawchak2026vvuq02}.}

\uscprov{1}{The unit economics are simple because the gate is deterministic:
cost in (compute for ten gates at three or more runs each, records storage,
and human review only on an ESCALATE), one cleared interaction class out, and
a ledger row written to the audit trail as section 515D(k) requires. Figure 9
draws the pipeline; Table 10 prices it.}

\begin{mermaidfig}
\node[mmin,text width=26mm]  (c1) at (0,0)    {Compute\\10 gates, 3+ runs each};
\node[mmin,text width=26mm]  (c2) at (0,-1.7) {Personnel\\review of ESCALATE only};
\node[mmin,text width=26mm]  (c3) at (0,-3.4) {Records\\hash-chained storage};
\node[mmstep,text width=28mm](g)  at (4.4,-1.7) {Ten-gate suite\\(verify, validate,\\quantify)};
\node[mmlaw,text width=26mm] (u)  at (8.6,0)    {Unit cost per cleared\\interaction class};
\node[mmlaw,text width=26mm] (l)  at (8.6,-1.7) {Cost ledger row\\(515D(k) record)};
\node[mmgoal,text width=26mm](s)  at (8.6,-3.6) {Annual aggregate\\to the Secretary};
\begin{scope}[on background layer]
\node[mmlane,fit=(c1)(c2)(c3),label={[mmlanetitle]above:Cost inputs (illustrative)}] {};
\node[mmlane,fit=(u)(l)(s),label={[mmlanetitle]above:Cost outputs}] {};
\end{scope}
\draw[mmedge] (c1) -- (g);
\draw[mmedge] (c2) -- (g);
\draw[mmedge] (c3) -- (g);
\draw[mmedge] (g) -- (u);
\draw[mmedge] (u) -- (l);
\draw[mmedge] (l) -- (s);
\end{mermaidfig}
\vspace{-0.7cm}
\figcaption{Figure 9. Unit economics of a ten-gate verification run: three cost inputs,\\one
deterministic suite, and the three cost outputs the bill makes load-bearing.}

{\footnotesize
\begin{xltabular}{\textwidth}{@{}L{8cm} Y R{1.9cm}@{}}
\hline\noalign{\vskip 0.04cm}
\textbf{Cost line (per cleared interaction class)} & \textbf{Traceable to} &
\textbf{Illustr.\ (\$)}\\
\hline\noalign{\vskip 0.04cm}
\endfirsthead
\hline\noalign{\vskip 0.04cm}
\textbf{Cost line (per cleared interaction class)} & \textbf{Traceable to} &
\textbf{Illustr.\ (\$)}\\
\hline\noalign{\vskip 0.04cm}
\endhead
\hline\noalign{\vskip 0.04cm}
\endlastfoot
Gates 01-05 (servo, force, balance, plan, grasp) & Table 2 rows 01-05; VVUQ-02
gate suite & 1,495\\
\hline\noalign{\vskip 0.04cm}
Gates 07, 08 (suturing, perception) & Table 2 rows 07-08 & 595\\
\hline\noalign{\vskip 0.04cm}
Hard-predicate gates 06, 09, 10 (no-fly, collision, fault) & Table 2 rows 06,
09, 10; catastrophe sim. & 1,620\\
\hline\noalign{\vskip 0.04cm}
Ten-gate compute subtotal & Sum of the Table 2 cost column & 3,710\\
\hline\noalign{\vskip 0.04cm}
Hash-chained records storage & 515D(e); 21 CFR part 11 trail & 240\\
\hline\noalign{\vskip 0.04cm}
Human review, amortized over ESCALATE rate & VVUQ-01 1-in-6 ESCALATE surface &
470\\
\hline\noalign{\vskip 0.04cm}
\textbf{Cost per cleared interaction class} & The 515D(k) ledger row &
\textbf{4,420}\\
\hline
\end{xltabular}}
\vspace{-0.7cm}
\figcaption{Table 10. The per-gate verification unit-cost schedule (illustrative,
seed 20260525): the\\Table 2 cost column composed into the cost per cleared
interaction class, with the three \\hard-predicate gates carrying the
catastrophe-simulation premium. The 1,495 + 595 +\\ 1,620 equals the 3,710 subtotal; with records and review the class clears at 4,420 dollars.}

\uscprov{1}{At program-year terms the comparison with the conventional path is
the financial case of finding (d). Operating the automated suite across an
investigation year - including re-verification on every change - costs
illustratively 155,000 dollars, against the 3,000,000 dollar conventional
ledger of Figure 2: a nineteen-fold reduction, with the four-work build
record itself (48,400 dollars, Table 1) a one-time cost smaller than two
percent of one conventional program-year. Table 11 reconciles the columns.}

{\footnotesize
\begin{xltabular}{\textwidth}{@{}Y R{2.6cm} R{2.6cm}@{}}
\hline\noalign{\vskip 0.04cm}
\textbf{Program-year line (illustrative)} & \textbf{Conventional (\$)} &
\textbf{Automated gate (\$)}\\
\hline\noalign{\vskip 0.04cm}
\endfirsthead
\hline\noalign{\vskip 0.04cm}
\textbf{Program-year line (illustrative)} & \textbf{Conventional (\$)} &
\textbf{Automated gate (\$)}\\
\hline\noalign{\vskip 0.04cm}
\endhead
\hline\noalign{\vskip 0.04cm}
\endlastfoot
Manual code review / suite operation & 1,800,000 & 96,000\\
\hline\noalign{\vskip 0.04cm}
Serial V\&V cycles / records and storage & 640,000 & 18,000\\
\hline\noalign{\vskip 0.04cm}
Re-review after each change / ESCALATE review & 310,000 & 41,000\\
\hline\noalign{\vskip 0.04cm}
Counsel and drafting overhead & 250,000 & -\\
\hline\noalign{\vskip 0.04cm}
\textbf{Total per program-year} & \textbf{3,000,000} & \textbf{155,000}\\
\hline\noalign{\vskip 0.04cm}
One-time four-work build record (Table 1) & - & 48,400\\
\hline
\end{xltabular}}
\vspace{-0.75cm}
\figcaption{Table 11. Acceleration economics summary (illustrative): the
conventional program-year ledger of\\Figure 2 beside the automated-gate
program-year, a nineteen-fold reduction, with the one-time\\four-work build
cost carried for completeness. Right-aligned R columns; every column sums.}
