%% ============================================================
%% sections/s4-comparative.tex
%% H. R. 9510 Bill v5.0 - SEC. 4. COMPARATIVE PRINT; CHANGES IN EXISTING LAW.
%% The comparative print, carried from Bill v3.0 and widened by one section for
%% the v5.0 financial layer: the convention statement, Table 4 (the per-section
%% change map, now twelve rows), Figure 5 (the twelve sections in
%% comparative-print order, ASCII), and the twelve affected Title 21 provisions
%% reproduced inline in 21 U.S.C. order - the eleven carried device sections
%% plus the user-fee section 379j amended by SEC. 5(c) - each showing only its
%% affected matter with insertions and deletions marked and omitted matter
%% shown by a row of asterisks.
%% ============================================================
% \clearpage
% \vspace{0.4cm}
\billsec{SEC. 4.}{COMPARATIVE PRINT; CHANGES IN EXISTING LAW.}\phantomsection\label{toc:s4}

\uscprov{1}{The following comparative print shows the changes proposed to existing
law by this Act. Matter proposed to be deleted is shown as \cprstrike{matter to be
deleted}; matter proposed to be inserted is shown as \cprinsert{matter to be
inserted}; existing law in which no change is proposed is shown as regular text,
and unchanged matter omitted for brevity is shown by a row of asterisks
\cite{usc-fdca, olrc-usc21}.}

\uscprov{1}{The comparative print reaches twelve Title 21 sections in 21
U.S.C. order - the eleven device sections carried from the prior versions plus
the user-fee section 379j amended by section 5(c) of this Act - each shown only
as to its affected provisions. Table 4 identifies every reproduced section, its
21 U.S.C. citation, the Federal Food, Drug, and Cosmetic Act section number, and
the change H. R. 9510 makes to it; Figure 5 lists the same twelve sections \cite{pl-119-93, usc-379j}.}

{\footnotesize
\begin{xltabular}{\textwidth}{@{}L{1.4cm} L{1.7cm} L{1.5cm} Y@{}}
\hline\noalign{\vskip 0.04cm}
\textbf{File} & \textbf{21 U.S.C.} & \textbf{FD\&C \S} & \textbf{Change made by
H. R. 9510}\\
\hline\noalign{\vskip 0.04cm}
\endfirsthead
\hline\noalign{\vskip 0.04cm}
\textbf{File} & \textbf{21 U.S.C.} & \textbf{FD\&C \S} & \textbf{Change made by
H. R. 9510}\\
\hline\noalign{\vskip 0.04cm}
\endhead
\hline\noalign{\vskip 0.04cm}
\endlastfoot
s301 & \S~301 & \S~1 & New ``Short Title of 2026 Amendment'' note\\
\hline\noalign{\vskip 0.04cm}
s321 & \S~321(h) & \S~201(h) & Device definition reaches software that generates
or executes robot-patient code\\
\hline\noalign{\vskip 0.04cm}
s331 & \S~331 & \S~301 & New prohibited act (jjj) for violating section 515D\\
\hline\noalign{\vskip 0.04cm}
s351 & \S~351 & \S~501 & New subsection (k): adulterated if used without a cleared
section 515D record\\
\hline\noalign{\vskip 0.04cm}
s355g & \S~355g & \S~505F & Real world evidence includes section 515D records; new
subsection (g)\\
\hline\noalign{\vskip 0.04cm}
s360 & \S~360(k) & \S~510(k) & A verification-governed change needs no new
premarket notification\\
\hline\noalign{\vskip 0.04cm}
s360c & \S~360c & \S~513 & New subsection (l): special controls graduated by
autonomy\\
\hline\noalign{\vskip 0.04cm}
s360e & \S~360e & \S~515 & New subparagraph (c)(1)(I): verification record in a PMA\\
\hline\noalign{\vskip 0.04cm}
s360e-4 & \S~360e-4 & \S~515C & Scope insertions and new subsection (d): the
keystone\\
\hline\noalign{\vskip 0.04cm}
s360j & \S~360j(o) & \S~520(o) & Robot-control software is not within the
clinical-decision-support exclusion\\
\hline\noalign{\vskip 0.04cm}
s360k & \S~360k & \S~521 & New subsection (c): savings clause for State
human-in-the-loop law\\
\hline\noalign{\vskip 0.04cm}
s379j & \S~379j & \S~738 & New paragraph (a)(4): a verif. record filed
alone: not a fee-bearing submission\\
\hline
\end{xltabular}}
\vspace{-0.5cm}
\figcaption{Table 4. Per-section comparative-print change map, twelve rows: each
reproduced section,\\its 21 U.S.C. citation, its Federal Food, Drug, and Cosmetic
Act section, and the change\\H. R. 9510 makes to it. The twelfth row is the v5.0
financial addition made by SEC. 5(c).}

\begin{asciifig}
 Twelve affected sections in 21 U.S.C. order (I = insertion, D = deletion)
---------------------------------------------------------------------------
  sec. 301     (s301)     [I]   short-title note: 2026 Amendment
  sec. 321(h)  (s321)     [I]   device definition reaches robot code
  sec. 331     (s331)     [I]   new prohibited act (jjj) for a 515D breach
  sec. 351     (s351)     [I]   new (k): adulterated without a record
  sec. 355g    (s355g)    [I]   real world evidence includes 515D records
  sec. 360(k)  (s360)     [I]   verification-governed change: no new 510(k)
  sec. 360c    (s360c)    [I]   new (l): special controls by autonomy
  sec. 360e    (s360e)    [I,D] new (c)(1)(I): verification record in a PMA
  sec. 360e-4  (s360e-4)  [I]   new (d): the keystone change-control rule
  sec. 360j(o) (s360j)    [I]   CDS exclusion does not reach robot code
  sec. 360k    (s360k)    [I]   new (c): savings clause for State review
  sec. 379j    (s379j)    [I]   new (a)(4): no fee for a verification
                                record filed alone (the v5.0 addition)
\end{asciifig}
\vspace{-0.4cm}
\figcaption{Figure 5. The twelve reproduced sections in comparative-print order
(ASCII), each marked as carrying an insertion, a deletion, or both. The same
pathway, with the financial sections, is drawn in Figure 4.}

\clearpage

\usccrosshead{CHANGES IN EXISTING LAW MADE BY THE BILL}
\begin{center}\small\itshape Federal Food, Drug, and Cosmetic Act (reproduced from
Title 21,\\United States Code, current through Public Law 119-93)\end{center}

% --- s301: 21 U.S.C. 301 (FD&C Act 1) Short title. ---
\uscsection{\S~301.}{Short title}

\uscprov{0}{This chapter may be cited as the Federal Food, Drug, and Cosmetic
Act.}

\begin{center}\small *\quad *\quad *\quad *\quad *\quad *\quad *\end{center}

\usccrosshead{Statutory Notes and Related Subsidiaries}

\uscnotehead{Short Title of 2025 Amendment}

\uscnotepar{Pub. L. 119-37, div. F, title V, \S~6501, Nov. 12, 2025, 139 Stat.
637, provided that: ``This title may be cited as the `Over-the-Counter Monograph
Drug User Fee Amendments'.''}

\uscnotehead{Short Title of 2026 Amendment}

\uscnotepar{\cprinsert{Pub. L. 119-\rule[0.5pt]{0.6cm}{0.4pt}, \S~1, approved in
2026, provided that: ``This Act may be cited as the `Verification Before
Generation in Physical AI Oncology Trials Act of 2026'.''}}

\begin{center}\small *\quad *\quad *\quad *\quad *\quad *\quad *\end{center}

% --- s321: 21 U.S.C. 321(h) (FD&C Act 201(h)) the device definition. ---
\uscsection{\S~321.}{Definitions; generally}

\begin{center}\small *\quad *\quad *\quad *\quad *\quad *\quad *\end{center}

\uscprov{1}{\textbf{(h)}}
\uscprov{2}{\textbf{(1)} The term ``device'' (except when used in paragraph (n)
of this section and in sections 331(i), 343(f), 352(c), and 362(c) of this
title) means an instrument, apparatus, implement, machine, contrivance, implant,
in vitro reagent, or other similar or related article, including any component,
part, or accessory, which is-}
\uscprov{3}{\textbf{(A)} recognized in the official National Formulary, or the
United States Pharmacopeia, or any supplement to them,}
\uscprov{3}{\textbf{(B)} intended for use in the diagnosis of disease or other
conditions, or in the cure, mitigation, treatment, or prevention of disease, in
man or other animals, or}
\uscprov{3}{\textbf{(C)} intended to affect the structure or any function of the
body of man or other animals, and}
\uscprov{2}{which does not achieve its primary intended purposes through chemical
action within or on the body of man or other animals and which is not dependent
upon being metabolized for the achievement of its primary intended purposes. The
term ``device'' does not include software functions excluded pursuant to section
360j(\textit{o}) of this title. \cprinsert{A software function that generates or
executes robot-patient interaction code (as defined in section 515D), or that
directs the autonomous physical action of a robot in contact with a human
subject in a clinical investigation, is a device and is not a software function
excluded under section 360j(o).}}

\begin{center}\small *\quad *\quad *\quad *\quad *\quad *\quad *\end{center}

% --- s331: 21 U.S.C. 331 (FD&C Act 301) prohibited acts. ---
\uscsection{\S~331.}{Prohibited acts}

\uscprov{0}{The following acts and the causing thereof are prohibited:}

\begin{center}\small *\quad *\quad *\quad *\quad *\quad *\quad *\end{center}

\uscprov{1}{\textbf{(hhh)} The failure to register or submit listing information
in accordance with section 364c of this title.}
\uscprov{1}{\textbf{(iii)} The refusal or failure to follow an order under
section 364g of this title.}
\uscprov{1}{\cprinsert{\textbf{(jjj)} The generation or execution of
robot-patient interaction code in a Physical AI oncology clinical investigation
in violation of section 515D, or the failure to make or file the documentation
and attestation required by section 515D before such generation or execution.}}

\begin{center}\small *\quad *\quad *\quad *\quad *\quad *\quad *\end{center}

% --- s351: 21 U.S.C. 351 (FD&C Act 501) adulterated drugs and devices. ---
\uscsection{\S~351.}{Adulterated drugs and devices}

\begin{center}\small *\quad *\quad *\quad *\quad *\quad *\quad *\end{center}

\uscprov{1}{\textbf{(h)}\textbf{ Manufacture, packing, storage, or installation
of device not in conformity with applicable requirements or conditions} If it is
a device and the methods used in, or the facilities or controls used for, its
manufacture, packing, storage, or installation are not in conformity with
applicable requirements under section 360j(f)(1) of this title or an applicable
condition prescribed by an order under section 360j(f)(2) of this title.}
\uscprov{1}{\textbf{(i)}\textbf{ Failure to comply with requirements under which
device was exempted for investigational use} If it is a device for which an
exemption has been granted under section 360j(g) of this title for
investigational use and the person who was granted such exemption or any
investigator who uses device under such exemption fails to comply with a
requirement prescribed by or under such section.}
\uscprov{1}{\textbf{(j)}\textbf{ Delayed, denied, or limited inspection; refusal
to permit entry or inspection} If it is a drug or device and it has been
manufactured, processed, packed, or held in any factory, warehouse, or
establishment and the owner, operator, or agent of such factory, warehouse, or
establishment delays, denies, or limits an inspection, or refuses to permit
entry or inspection.}
\uscprov{1}{\cprinsert{\textbf{(k)}\textbf{ Physical AI device software function
used without a cleared verification record} If it is a Physical AI device
software function (as defined in section 515D) used to generate or execute
robot-patient interaction code in a clinical investigation without a cleared
verification record required by section 515D, or in a manner not in conformity
with a predetermined change control plan governed by section 515D.}}
\uscprov{1}{For purposes of paragraph (a)(2)(B), the term ``current good
manufacturing practice'' includes the implementation of oversight and controls
over the manufacture of drugs to ensure quality, including managing the risk of
and establishing the safety of raw materials, materials used in the
manufacturing of drugs, and finished drug products.}

\begin{center}\small *\quad *\quad *\quad *\quad *\quad *\quad *\end{center}

% --- s355g: 21 U.S.C. 355g (FD&C Act 505F) utilizing real world evidence. ---
\uscsection{\S~355g.}{Utilizing real world evidence}

\uscprov{1}{\textbf{(a)}\textbf{ In general} The Secretary shall establish a
program to evaluate the use of real world evidence-}
\uscprov{2}{\textbf{(1)} to help to support the approval of a new indication for
a drug approved under section 355(c) of this title; and}
\uscprov{2}{\textbf{(2)} to help to support or satisfy postapproval study
requirements.}
\uscprov{1}{\textbf{(b)}\textbf{ Real world evidence defined} In this section,
the term ``real world evidence'' means data regarding the usage, or the
potential benefits or risks, of a drug derived from sources other than
traditional clinical trials. \cprinsert{Such term includes verification,
validation, and uncertainty quantification records and trial telemetry generated
under section 515D.}}

\begin{center}\small *\quad *\quad *\quad *\quad *\quad *\quad *\end{center}

\uscprov{1}{\cprinsert{\textbf{(g)}\textbf{ Application to Physical AI oncology
investigations} The Secretary shall, in carrying out the program under this
section, evaluate the use of real world evidence, including records generated
under section 515D, to support the evaluation of devices used in Physical AI
oncology clinical investigations.}}

% --- s360: 21 U.S.C. 360(k) (FD&C Act 510(k)) the 510(k) pathway. ---
\uscsection{\S~360.}{Registration of producers of drugs or devices}

\begin{center}\small *\quad *\quad *\quad *\quad *\quad *\quad *\end{center}

\uscprov{1}{\textbf{(k)}\textbf{ Report preceding introduction of devices into
interstate commerce} Each person who is required to register under this section
and who proposes to begin the introduction or delivery for introduction into
interstate commerce for commercial distribution of a device intended for human
use shall, at least ninety days before making such introduction or delivery,
report to the Secretary or person who is accredited under section 360m(a) of
this title (in such form and manner as the Secretary shall by regulation
prescribe)-}
\uscprov{2}{\textbf{(1)} the class in which the device is classified under
section 360c of this title or if such person determines that the device is not
classified under such section, a statement of that determination and the basis
for such person's determination that the device is or is not so classified, and}
\uscprov{2}{\textbf{(2)} action taken by such person to comply with requirements
under section 360d or 360e of this title which are applicable to the device.}
\uscprov{1}{A notification submitted under this subsection that contains clinical
trial data for an applicable device clinical trial (as defined in section
282(j)(1) of title 42) shall be accompanied by the certification required under
section 282(j)(5)(B) of such title. Such certification shall not be considered
an element of such notification. \cprinsert{A change to a device that generates
or executes robot-patient interaction code, cleared under this subsection, that
is consistent with a verification protocol under section 515D and an established
predetermined change control plan under section 360e-4, shall not require a new
premarket notification under this subsection.}}

\begin{center}\small *\quad *\quad *\quad *\quad *\quad *\quad *\end{center}

% --- s360c: 21 U.S.C. 360c (FD&C Act 513) classification of devices. ---
\uscsection{\S~360c.}{Classification of devices intended for human use}

\uscprov{1}{\textbf{(a)}\textbf{ Classes of devices}}
\uscprov{2}{\textbf{(1)} There are established the following classes of devices
intended for human use:}

\begin{center}\small *\quad *\quad *\quad *\quad *\quad *\quad *\end{center}

\uscprov{3}{\textbf{(B)}\textbf{ Class II, Special Controls.-} A device which
cannot be classified as a class I device because the general controls by
themselves are insufficient to provide reasonable assurance of the safety and
effectiveness of the device, and for which there is sufficient information to
establish special controls to provide such assurance, including the promulgation
of performance standards, postmarket surveillance, patient registries,
development and dissemination of guidelines (including guidelines for the
submission of clinical data in premarket notification submissions in accordance
with section 360(k) of this title), recommendations, and other appropriate
actions as the Secretary deems necessary to provide such assurance.}

\begin{center}\small *\quad *\quad *\quad *\quad *\quad *\quad *\end{center}

\uscprov{1}{\cprinsert{\textbf{(l)}\textbf{ Physical AI device software
functions} In classifying a device that generates or executes robot-patient
interaction code, the Secretary shall consider the degree of autonomy of the
device (assistive, augmentative, or autonomous) and may establish special
controls, including a verification protocol under section 515D, commensurate with
that degree of autonomy. A device of autonomous degree used in a Physical AI
oncology clinical investigation shall be subject to the verification requirements
of section 515D regardless of class.}}

% --- s360e: 21 U.S.C. 360e (FD&C Act 515) premarket approval. ---
\uscsection{\S~360e.}{Premarket approval}

\begin{center}\small *\quad *\quad *\quad *\quad *\quad *\quad *\end{center}

\uscprov{1}{\textbf{(c)}\textbf{ Application for premarket approval}}
\uscprov{2}{\textbf{(1)} Any person may file with the Secretary an application
for premarket approval for a class III device. Such an application for a device
shall contain-}

\begin{center}\small *\quad *\quad *\quad *\quad *\quad *\quad *\end{center}

\uscprov{3}{\textbf{(G)} the certification required under section 282(j)(5)(B) of
title 42 (which shall not be considered an element of such application);\cprstrike{ and}}
\uscprov{3}{\textbf{(H)} such other information relevant to the subject matter of
the application as the Secretary, with the concurrence of the appropriate panel
under section 360c of this title, may require\cprstrike{.}\cprinsert{; and}}
\uscprov{3}{\cprinsert{\textbf{(I)} in the case of a device that generates or
executes robot-patient interaction code, the cleared verification record and the
gate evidence required by section 515D.}}

\begin{center}\small *\quad *\quad *\quad *\quad *\quad *\quad *\end{center}

% --- s360e-4: 21 U.S.C. 360e-4 (FD&C Act 515C) predetermined change control. ---
\uscsection{\S~360e-4.}{Predetermined change control plans for devices}

\uscprov{1}{\textbf{(a)}\textbf{ Approved devices}}
\uscprov{2}{\textbf{(1)}\textbf{ In general} Notwithstanding section
360e(d)(5)(A) of this title, a supplemental application shall not be required for
a change to a device approved under section 360e of this title, if such change
is consistent with a PCCP that is approved pursuant
to paragraph (2).}
\uscprov{2}{\textbf{(2)}\textbf{ Predetermined change control plan} The Secretary
may approve a predetermined change control plan submitted in an application,
including a supplemental application, under section 360e of this title that
describes planned changes that may be made to the device (and that would
otherwise require a supplemental application under section 360e of this title),
if the device remains safe and effective without any change.}
\uscprov{2}{\textbf{(3)}\textbf{ Scope} The Secretary may require that a change
control plan include labeling required for safe and effective use of the device
as such device changes pursuant to such plan, notification requirements if the
device does not function as intended pursuant to such plan, and performance
requirements for changes made under the plan\cprinsert{, and, for a device that
generates or executes robot-patient interaction code, an automated
verification-before-change protocol consistent with section 515D that must clear
before any change is implemented}.}
\uscprov{1}{\textbf{(b)}\textbf{ Cleared devices}}
\uscprov{2}{\textbf{(1)}\textbf{ In general} Notwithstanding section 360(k) of
this title, a premarket notification shall not be required for a change to a
device cleared under section 360(k) of this title, if such change is consistent
with an established PCCP granted pursuant to
paragraph (2).}
\uscprov{2}{\textbf{(2)}\textbf{ Predetermined change control plan} The Secretary
may clear a PCCP submitted in a notification
submitted under section 360(k) of this title that describes planned changes that
may be made to the device (and that would otherwise require a new notification),
if-}
\uscprov{3}{\textbf{(A)} the device remains safe and effective without any such
change; and}
\uscprov{3}{\textbf{(B)} the device would remain substantially equivalent to the
predicate.}
\uscprov{2}{\textbf{(3)}\textbf{ Scope} The Secretary may require that a change
control plan include labeling required for safe and effective use of the device
as such device changes pursuant to such plan, notification requirements if the
device does not function as intended pursuant to such plan, and performance
requirements for changes made under the plan\cprinsert{, and, for a device that
generates or executes robot-patient interaction code, an automated
verification-before-change protocol consistent with section 515D that must clear
before any change is implemented}.}
\uscprov{1}{\textbf{(c)}\textbf{ Predicate devices} In making a determination of
substantial equivalence pursuant to section 360c(i) of this title, the Secretary
shall not compare a device to changed versions of a device implemented in
accordance with an established predetermined change control plan as a predicate
device. Only the version of the device cleared or approved, prior to changes made
under the predetermined change control plan, may be used by a sponsor as a
predicate device.}
\uscprov{1}{\cprinsert{\textbf{(d)}\textbf{ Physical AI device software functions}
A predetermined change control plan for a device that generates or executes
robot-patient interaction code shall require that each planned change clear the
verification process required by section 515D, in advance of generation or
execution, as a condition of being implemented without a new submission under
section 360e or section 360(k).}}

% --- s360j: 21 U.S.C. 360j(o) (FD&C Act 520(o)) the CDS exclusion. ---
\uscsection{\S~360j.}{General provisions respecting control of devices intended
for human use}

\begin{center}\small *\quad *\quad *\quad *\quad *\quad *\quad *\end{center}

\uscprov{1}{\textbf{(o)}\textbf{ Regulation of medical and certain decisions
support software}}
\uscprov{2}{\textbf{(1)} The term ``device'', as defined in section 321(h) of
this title, shall not include a software function that is intended-}

\begin{center}\small *\quad *\quad *\quad *\quad *\quad *\quad *\end{center}

\uscprov{3}{\textbf{(E)} unless the function is intended to acquire, process, or
analyze a medical image or a signal from an in vitro diagnostic device or a
pattern or signal from a signal acquisition system, for the purpose of-}
\uscprov{4}{\textbf{(i)} displaying, analyzing, or printing medical information
about a patient or other medical information (such as peer-reviewed clinical
studies and clinical practice guidelines);}
\uscprov{4}{\textbf{(ii)} supporting or providing recommendations to a health
care professional about prevention, diagnosis, or treatment of a disease or
condition; and}
\uscprov{4}{\textbf{(iii)} enabling such health care professional to
independently review the basis for such recommendations that such software
presents so that it is not the intent that such health care professional rely
primarily on any of such recommendations to make a clinical diagnosis or
treatment decision regarding an individual patient.}
\uscprov{2}{\cprinsert{The exclusion in this paragraph does not apply to, and the
term ``device'' includes, a software function that generates or executes
robot-patient interaction code, or that directs the autonomous physical action of
a robot in contact with a human subject in a clinical investigation; such a
function is a device subject to section 515D.}}

\begin{center}\small *\quad *\quad *\quad *\quad *\quad *\quad *\end{center}

% --- s360k: 21 U.S.C. 360k (FD&C Act 521) State and local requirements. ---
\uscsection{\S~360k.}{State and local requirements respecting devices}

\uscprov{1}{\textbf{(a)}\textbf{ General rule} Except as provided in subsection
(b), no State or political subdivision of a State may establish or continue in
effect with respect to a device intended for human use any requirement-}
\uscprov{2}{\textbf{(1)} which is different from, or in addition to, any
requirement under this chapter to the device, and}
\uscprov{2}{\textbf{(2)} which relates to the safety or effectiveness of the
device or to any other matter included in a requirement applicable to the device
under this chapter.}
\uscprov{1}{\textbf{(b)}\textbf{ Exempt requirements} Upon application of a State
or a political subdivision thereof, the Secretary may, by regulation promulgated
after notice and opportunity for an oral hearing, exempt from subsection (a),
under such conditions as may be prescribed in such regulation, a requirement of
such State or political subdivision applicable to a device intended for human use
if-}
\uscprov{2}{\textbf{(1)} the requirement is more stringent than a requirement
under this chapter which would be applicable to the device if an exemption were
not in effect under this subsection; or}
\uscprov{2}{\textbf{(2)} the requirement-}
\uscprov{3}{\textbf{(A)} is required by compelling local conditions, and}
\uscprov{3}{\textbf{(B)} compliance with the requirement would not cause the
device to be in violation of any applicable requirement under this chapter.}
\uscprov{1}{\cprinsert{\textbf{(c)}\textbf{ Rule of construction for Physical AI
oversight} Nothing in this section preempts a State requirement of general
applicability that a licensed human retain the authority to monitor, intervene,
override, or terminate an artificial intelligence or robotic system, or that an
audit record be maintained, to the extent that the requirement is not different
from, or in addition to, a requirement applicable under this chapter to a
device, including the verification requirements of section 515D.}}

\begin{center}\small *\quad *\quad *\quad *\quad *\quad *\quad *\end{center}

% --- s379j: 21 U.S.C. 379j (FD&C Act 738) device user fees (the v5.0 row). ---
\uscsection{\S~379j.}{Authority to assess and use device fees}

\uscprov{1}{\textbf{(a)}\textbf{ Types of fees} Beginning on October 1, 2022,
the Secretary shall assess and collect fees in accordance with this section.}

\begin{center}\small *\quad *\quad *\quad *\quad *\quad *\quad *\end{center}

\uscprov{1}{\cprinsert{\textbf{(a)(4)}\textbf{ Verification records} No fee
shall be assessed under this section for the filing of a verification record,
or of a verification cost record, under section 360e-5 of this title, and such
a filing, alone, shall not constitute a submission for which a fee is due
under this section. Nothing in this paragraph reduces or displaces the fee due
for a premarket application, premarket report, supplement, premarket
notification submission, or submission that a verification
record accompanies.}}

\begin{center}\small *\quad *\quad *\quad *\quad *\quad *\quad *\end{center}
