%% sections/s2-findings.tex - H. R. 9510 Bill v4.0 (draft scaffold)
%% SEC. 2. FINDINGS; THE EVIDENCE TO LAW RECORD.
\billsec{SEC. 2.}{FINDINGS; THE EVIDENCE TO LAW RECORD.}\phantomsection\label{toc:s2}

\uscprov{1}{\textbf{(a) In General.} Congress finds that an automated process must
verify robot-patient interaction code before that code is generated or executed in
a Physical AI oncology clinical investigation, and that the record of the VVUQ-01
through VVUQ-04 developments establishes both the need for and the feasibility of
that requirement.}

\uscprov{0}{[DRAFTING INSTRUCTIONS - SEC. 2. Render the fourteen findings of Bill
v2.0 as a lettered narrative (a) through (g) carried by three visuals, in place of
a long numbered list. Process
\texttt{cancer-automated/.../VVUQ-05/final-bill/sections/s2-findings.tex} for the
finding text and \texttt{.../deliverables/04-legislative-findings.md} for the
authorities. Render Figure 1 (four-work evidence-to-law lineage, gray-scale Mermaid
flowchart LR), Table 1 (the four works at a glance, full-width), and Figure 2
(accelerated timeline versus conventional, paired flowchart) per
\texttt{auto-bill-01/04-figure-selection}. Bind findings to in-force authorities:
section 515C / 21 U.S.C. 360e-4, the QMSR (part 820), ASME V\&V 40, ISO/TS 15066,
NASA-STD-7009A, the Medicare Advantage AI guardrail, and the State human-over-AI
statutes.]}

\uscprov{1}{[FIGURE 1 SLOT - four-work lineage. TABLE 1 SLOT - four works at a
glance. FIGURE 2 SLOT - accelerated timeline. Each is rendered in the full bill.]}
